### 2011-05-06 paper/paper.tex
drafted conclusion

\begin{theorem}[{\bf Hit-and-run bound}] Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $P$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - P(r)| \le \epsilon$.\end{center}
\end{theorem}

@@

\subsection{The regions}

@@

\subsection{The sampling}

For each sampling method and for each test case, we generated $1000$ samples. In most cases, we used $5000$ iterations of our random walk's transition function in order to generate each sample. However, as noted above, the hit-and-run method is slower due to its binary search. We binary search up to a precision of $10^{-12}$, which requires approximately $40$ calls to the membership oracle for each endpoint. We found empirically that transitioning only $1200$ times caused the program to run in about as much time as the other methods on $5000$ transitions. Therefore, we also ran tests with only $1200$ transitions for the hit-and-run.

@@

>>>>

\begin{theorem}[{\bf Hit-and-run bound}] \label{hitandrunbound} Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $P$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - P(r)| \le \epsilon$.\end{center}
\end{theorem}

@@

\subsection{The Regions (test cases)}

@@

\subsection{The Sampling}

For each sampling method and for each test case, we generated $1000$ samples. In most cases, we used $5000$ iterations of our random walk's transition function in order to generate each sample. However, as noted above, the hit-and-run method is slower due to its binary search. We binary search up to a precision of $10^{-12}$, which requires approximately $40$ calls to the membership oracle for each endpoint. We found empirically that transitioning only $1200$ times caused the program to run in about as much time as the other methods on $5000$ transitions. Therefore, we also ran tests with only $1200$ transitions for the hit-and-run. We also ran Gaussian-walking and adapative Gaussian-walking at $2000$ iterations for comparison between the two.

@@

In conclusion, we have found that the results of our tests confirm what we thought to be theoretically true: the hit-and-run method performs much better than the Metropolis methods. With a good start, hit-and-run required only something on the order of $1000$ iterations to produce a distribution that seemed reasonably uniform, which is even better than the bound given in \ref{hitandrunbound}, even with $100$ dimensions, whereas this cube is too larger for the the basic-ball walking method to have a good chance of even reaching the edges. We also saw that the basic Gaussian-walking method worked better than the ball-walking method in this case.

In general, the adaptive methods performed better than their non-adaptive counterparts. When started from the corner of a cube or a simplex, the non-adaptive methods would always stay in that corner for high-dimension test cases, even $n=10$. The adaptive methods, however, produced a distribution which looked much more uniform.

These results indicate that, in practice, the hit-and-run method is better than the Metropolis methods, even when taking into account its slower transition step. Among the Metropolis methods, the Gaussian-walking method is a slight improvement over the ball-walking method, and the adaptive methods always help in cases where are starting point is near a corner.
